Screen Time Review of Reviews Summary

### 2021-05-14 report.Rmd
First pass update on report and update to targets.

---
title: "Report on Effect Size Translation"
ipsum_meta:
  twitter_card: "Summary info for the Twitter Card"
  twitter_site: "\\@sitehandle"
  twitter_creator: "\\@creatorhandle"
  og_url: "https\\://example.com/open/graph/finalURLfor/this"
  og_description: "A modest size description of the content"
  og_image: "https\\://example.com/open/graph/imageURLfor/this"
output: 
  hrbrthemes::ipsum:
    toc: true
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.retina=2, echo=FALSE,message = FALSE,
                      warnings=FALSE, error = FALSE)
```

```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
library(hrbrthemes)
library(tidyverse)
library(targets)
library(gt)

update_geom_font_defaults(font_rc)
```

>>>>

---
title: "Screen Time Review of Reviews Summary"
output:
  rmdformats::html_clean:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    fig_caption: true
    use_bookdown: true
    number_sections: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.retina=2
)
```

```{r}
library(hrbrthemes)
library(tidyverse)
library(targets)
library(gt)

update_geom_font_defaults(font_rc)

# Results

## Review Characteristics

```{r}
source("R/reviews_table.R")
review_table_DT
```

#### Kable
```{r}
review_table_kable
```

## PRISMA Diagram

```{r}
source("R/PRISMA.R")
DiagrammeR::grViz(prisma)
```

## Forest Plots {.tabset}

###
